Distances between histograms

### 2015-10-28 tables/tabNormNull.tex
finished examples with texts

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 4 & 7 & 7 \\\hline
5.0 & 0.050 & 1.36 & 2 & 5 & 3 \\\hline
2.5 & 0.025 & 1.48 & 1 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7144$ and $\sigma(c_1')=0.2661$,
 $\mu(c_2')=0.7261$ and $\sigma(c_2')=0.2768$,
 $\mu(c_3')=0.7379$ and $\sigma(c_3')=0.2647$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 6 & 2 & 4 \\\hline
5.0 & 0.050 & 1.36 & 3 & 0 & 3 \\\hline
2.5 & 0.025 & 1.48 & 1 & 0 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7240$ and $\sigma(c_1')=0.2850$,
 $\mu(c_2')=0.7079$ and $\sigma(c_2')=0.2314$,
 $\mu(c_3')=0.7187$ and $\sigma(c_3')=0.2559$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabPowerNull.tex
finished examples with texts

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ & $|C_5'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 4 & 11 & 3 & 7 & 6 \\\hline
5.0 & 0.050 & 1.36 & 2 & 5 & 1 & 3 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 power functions distributions with $a=0.3$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 power functions distributions with $a=1$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 power functions distributions with $a=2$.
The $N_o$ values of $c_4'$ were calculated using simulations of
 power functions distributions with $a=3$.
The $N_o$ values of $c_5'$ were calculated using simulations of
 power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7220$ and $\sigma(c_1')=0.2649$,
 $\mu(c_2')=0.7992$ and $\sigma(c_2')=0.2704$,
 $\mu(c_3')=0.7294$ and $\sigma(c_3')=0.2361$ .
 $\mu(c_4')=0.7629$ and $\sigma(c_4')=0.2565$ .
 $\mu(c_5')=0.7182$ and $\sigma(c_5')=0.2753$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ & $|C_5'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 4 & 10 & 7 & 9 & 1 \\\hline
5.0 & 0.050 & 1.36 & 3 & 3 & 4 & 5 & 0 \\\hline
2.5 & 0.025 & 1.48 & 1 & 1 & 2 & 3 & 0 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 1 & 2 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 power functions distributions with $a=0.3$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 power functions distributions with $a=1$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 power functions distributions with $a=2$.
The $N_o$ values of $c_4'$ were calculated using simulations of
 power functions distributions with $a=3$.
The $N_o$ values of $c_5'$ were calculated using simulations of
 power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7343$ and $\sigma(c_1')=0.2654$,
 $\mu(c_2')=0.8139$ and $\sigma(c_2')=0.2698$,
 $\mu(c_3')=0.7328$ and $\sigma(c_3')=0.2731$ .
 $\mu(c_4')=0.7623$ and $\sigma(c_4')=0.3053$ .
 $\mu(c_5')=0.7269$ and $\sigma(c_5')=0.1949$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabUniformNull.tex
finished examples with texts

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 3 & 4 \\\hline
5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
2.5 & 0.025 & 1.48 & 2 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7967$ and $\sigma(c_1')=0.2597$,
 $\mu(c_2')=0.7600$ and $\sigma(c_2')=0.2435$,
 $\mu(c_3')=0.7252$ and $\sigma(c_3')=0.2263$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 8 & 10 & 6 \\\hline
5.0 & 0.050 & 1.36 & 6 & 3 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7965$ and $\sigma(c_1')=0.2768$,
 $\mu(c_2')=0.7773$ and $\sigma(c_2')=0.2657$,
 $\mu(c_3')=0.7828$ and $\sigma(c_3')=0.2589$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabWeibullNull.tex
finished examples with texts

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 2 & 6 & 5 \\\hline
5.0 & 0.050 & 1.36 & 0 & 2 & 3 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0622$ and $\sigma(c_1')=0.0397$,
 $\mu(c_2')=0.6934$ and $\sigma(c_2')=0.2186$,
 $\mu(c_3')=0.7638$ and $\sigma(c_3')=0.2684$ .
 $\mu(c_4')=0.7283$ and $\sigma(c_4')=0.2810$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 8 & 3 & 10 \\\hline
5.0 & 0.050 & 1.36 & 0 & 5 & 3 & 7 \\\hline
2.5 & 0.025 & 1.48 & 0 & 3 & 3 & 4 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 1 & 3 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0646$ and $\sigma(c_1')=0.0373$,
 $\mu(c_2')=0.7737$ and $\sigma(c_2')=0.2842$,
 $\mu(c_3')=0.6977$ and $\sigma(c_3')=0.2629$ .
 $\mu(c_4')=0.7782$ and $\sigma(c_4')=0.3116$ .
}
\end{center}
\end{table}
